Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-07 latex/comp_or.tex
Second paper update

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 9.66         &  6.38       &  9.55       &  11.12      &  12.37      &   12.03      & 0.89 \\% 6111
&                                                & {\it run-time (s)} &  < 1         &  5          &    11       &   43        &  128        &  835         &  1.0 \\% 1023

@@

&                                                & {\it run-time (s)} &  < 1         &  2          &    4        &  15         &  47         & 295          &  {\bf 2.8}\\% 364

@@

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 13.70        &  9.07       &  13.70      &  15.43      &   17.19     &  17.24       & 0.87 \\%8633
&                                                & {\it run-time (s)} &  < 1         &  4          &    7        &   26        &   81        &  520         & 1.0\\% 639

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 14.82        & 10.45       & 17.45       &{\bf 16.92}  & 19.27       & 18.30        & 0.98\\%9721
&                                                & {\it run-time (s)} &  < 1         &  2          &    3        &    12       &   38        &   236        & {\bf 2.2}\\% 292

@@

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                &   20.42      &   13.90     &  20.30      &  22.96      &   25.28     &   24.81      & 0.91\\% 12767
&                                                & {\it run-time (s)} &  2           &  9          &    17       &   68        &   206       &  1216        & 1.0\\% 1518

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                &  22.66       &  15.41      &  23.17      &  23.37      &  23,91      &  25.25       &  0.96\\% 13377
&                                                & {\it run-time (s)} &  2           &  3          &    5        &   20        &   64        &  398         & {\bf 2.8}\\% 544

@@

{\it mpShims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, mpShims was 2.6 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the runtime {\it race condition} management limited {\it mpShims} performance.

@@

Another important contribution is that we employed the {\it iRace} package \citep{LopezIbanezManuel2016} to fine tune the meta-heuristics parameters, guaranteeing the best possible performance for the instances under training and testing.

>>>>

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 9.66         &  6.38       &  9.55       &  11.12      &  12.37      &   12.03      & 0.89 \\% 6111
&                                                & {\it run time (s)} &  < 1         &  5          &    11       &   43        &  128        &  835         &  1.0 \\% 1023

@@

&                                                & {\it run time (s)} &  < 1         &  2          &    4        &  15         &  47         & 295          &  {\bf 2.8}\\% 364

@@

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 13.70        &  9.07       &  13.70      &  15.43      &   17.19     &  17.24       & 0.87 \\%8633
&                                                & {\it run time (s)} &  < 1         &  4          &    7        &   26        &   81        &  520         & 1.0\\% 639

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 14.82        & 10.45       & 17.45       &{\bf 16.92}  & 19.27       & 18.30        & 0.98\\%9721
&                                                & {\it run time (s)} &  < 1         &  2          &    3        &    12       &   38        &   236        & {\bf 2.2}\\% 292

@@

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                &   20.42      &   13.90     &  20.30      &  22.96      &   25.28     &   24.81      & 0.91\\% 12767
&                                                & {\it run time (s)} &  2           &  9          &    17       &   68        &   206       &  1216        & 1.0\\% 1518

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                &  22.66       &  15.41      &  23.17      &  23.37      &  23,91      &  25.25       &  0.96\\% 13377
&                                                & {\it run time (s)} &  2           &  3          &    5        &   20        &   64        &  398         & {\bf 2.8}\\% 544

@@

{\it mpShims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, mpShims was 2.6 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the run-time {\it race condition} management limited {\it mpShims} performance.

@@

Another important contribution is that we employed the {\it iRace} package \citep{LopezIbanezManuel2016} to fine tune the {\it mpShims} parameters, guaranteeing the best possible performance for the instances under training and testing.
